A Cross-Benchmark Comparison of 87 Learning to Rank Methods

### 2014-09-02 paper/ECIR/paper.tex
ECIR paper :)

\documentclass{llncs}
\usepackage{llncsdoc}
\usepackage{booktabs}
\usepackage{multicol}
\usepackage{amsmath}
\usepackage{longtable}
\usepackage{graphicx}
\usepackage{dblfloatfix}
\usepackage{fixltx2e}
\usepackage{enumitem}
\usepackage{float}
\renewcommand{\dblfloatpagefraction}{2.0}
\usepackage{array}
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\usepackage{balance}
\begin{document}

\title{A Cross-Benchmark Comparison of 87 Learning to Rank Methods}

\author{First Author\inst{1,2} \and Second Author\inst{1} \and Third Author\inst{2}}

\authorrunning{First Author et al.} % abbreviated author list (for running head)

%%%% list of authors for the TOC (use if author list has to be modified)
\tocauthor{First Author, Second Author, Third Author}

\institute{Blinded Institute 1, Adress Line 1, Address Line 2, County\\
\email{first.author@institute.com},\\
\and
Blinded Institute 2, Address Line 1, Address Line 2, Country}

%\author{Niek Tax\inst{1,2} \and Sander Bockting\inst{1} \and Djoerd Hiemstra\inst{2}}
%
%\authorrunning{Niek Tax et al.} % abbreviated author list (for running head)
%
%%%% list of authors for the TOC (use if author list has to be modified)
%\tocauthor{Niek Tax, Sander Bockting, Djoerd Hiemstra}
%
%\institute{Avanade Netherlands B.V., Versterkerstraat 6, 1322 AP Almere, the Netherlands\\
%\email{niek.tax@avanade.com},\\
%\and
%University of Twente, P.O. Box 217, 7500AE Enschede, the Netherlands}

\maketitle
\begin{abstract}
Learning to rank is an increasingly important scientific field that comprises the use of machine learning for the ranking task. New learning to rank methods are generally evaluated on benchmark test collections. However, comparison of learning to rank methods based on evaluation results is hindered by non-existence of a standard set of evaluation benchmark collections. In this paper we propose a way to compare learning to rank methods based on a sparse set of evaluation results on a set of benchmark datasets. Our comparison methodology consists of two components: 1) Normalized Winning Number, which gives insight in the ranking accuracy of the learning to rank method, and 2) Ideal Winning Number, which gives insight in the degree of certainty concerning its ranking accuracy. Evaluation results of 87 learning to rank methods on 20 well-known benchmark datasets are collected through a structured literature search. ListNet, SmoothRank, FenchelRank, FSMRank, LRUF and LARF are the best performing learning to rank methods in increasing order of Normalized Winning Number and decreasing order of Ideal Winning Number.
\end{abstract}

@@

\section{Introduction}
Ranking is a core problem in the field of information retrieval. The ranking task in information retrieval entails the ranking of candidate documents according to their relevance to a given query. Ranking has become a vital part of web search, where commercial search engines help users find their need in the extremely large collection of the World Wide Web. Among useful applications outside web search are automatic text summarization, machine translation, drug discovery and determining the ideal order of maintenance operations \cite{Rudin2009}. In addition, the ranking task has been argued to be a better fit for recommender systems than the regression task \cite{McNee2006} (which concerns predictions on a continuous scale) that is currently frequently used in such systems.\\

@@

\section{Collecting Evaluation Results}
\label{sec:collecting_evaluation_results}
We collect evaluation results on the datasets of benchmark collections through a structured literature search. Table \ref{tbl:ltr_benchmark_collections} presents an overview of the benchmark collections included in the meta-analysis.

\begin{table}[!h]
\scriptsize{
\begin{tabular}{p{6.4cm}R{1.26cm}}\toprule
Benchmark collection & \# of datasets \\
\midrule
AOL		  & 1\\
LETOR 2.0 & 3\\
LETOR 3.0 & 7\\
LETOR 4.0 & 2\\
MSLR	  & 2\\
WCL2R	  & 2\\
Yahoo! Learning to Rank Challenge 	     & 2\\
Yandex Internet Mathematics 2009 contest & 1\\
\textbf{Total} & \textbf{20}\\ 	
\bottomrule
\end{tabular}
\caption{Included learning to rank evaluation benchmark collections}
\label{tbl:ltr_benchmark_collections}}
\end{table}

@@

LETOR 1.0 and 3.0, Yahoo! Learning to Rank Challenge, WCL2R and AOL have accompanying papers that were released with the collection. Authors publishing evaluation results on these benchmark collections are requested to cite these papers. We collect evaluation measurements of learning to rank methods on these benchmark collections through forward literature search. Table~\ref{tbl:ltr_benchmark_forref} presents an overview of the results of this forward literature search performed using Google Scholar.
\begin{table}[!h]
\scriptsize{
\begin{tabular}{p{2.8cm}p{2.64cm}R{1.9cm}}\toprule
Benchmark & Paper & \# of forward references \\
\midrule
LETOR 1.0 \& 2.0 & Liu et al. \cite{Liu2007b} & 307\\
LETOR 3.0 & Qin et al. \cite{Qin2010} & 105\\
Yahoo! Learning to Rank Challenge & Chapelle et al. \cite{Chapelle2011a} & 102\\
AOL dataset & Pass et al. \cite{Pass2006} & 339\\
WCL2R & Alc{\^a}ntara et al. \cite{Alcantara2010} & 2\\
\bottomrule
\end{tabular}
\caption{Forward references of learning to rank benchmark papers}
\label{tbl:ltr_benchmark_forref}}
\end{table}

The LETOR 4.0, MSLR-web10/30k and Yandex Internet Mathematics Competition 2009 benchmark collections are not accompanied by a paper. To collect evaluation results for learning to rank methods on these benchmarks, a Google Scholar search is performed on the name of the benchmark. Table~\ref{tbl:ltr_benchmark_searches} shows the results of this literature search.

\begin{table}[!h]
\scriptsize{
\begin{tabular}{p{5.2cm}R{2.5cm}}\toprule
Search Query & Google scholar search results \\
\midrule
"LETOR 4.0" & 75 \\
"MSLR-web10k" & 16 \\
"MSLR-web30k" & 15 \\
"Yandex Internet Mathematics" & 3\\
\bottomrule
\end{tabular}
\caption{Google scholar search results for learning to rank benchmarks}
\label{tbl:ltr_benchmark_searches}}
\end{table}

\subsection{Literature Selection}
Table 4 in the appendix gives an overview of the learning to rank methods for which evaluation results were found through the described procedure. Occurrences of L2, L3 and L4 in Table 4 imply that these algorithms are evaluated as official LETOR 2.0, 3.0 and 4.0 baselines respectively.\\

@@

\begin{enumerate}[noitemsep,nolistsep]
\item A different evaluation methodology was used in the study compared to what was used in other studies using the same benchmark \cite{Geng2011,Lin2012}
\item The study focuses on a different learning to rank task (e.g. rank aggregation or transfer ranking) \cite{De2011,De2010,Derhami2013,De2012,Chen2010,Ah-Pine2008,Wang2009c,De2013,Miao2013,Hoi2008,De2012b,Duh2011b,Argentini2012,Qin2010c,Volkovs2013,Desarkar2011,Pan2013,Lin2011b,Volkovs2012,Dammak2011}
\item The study used an altered version of a benchmark that contained additional features \cite{Bidoki2009,Ding2010}
\item The study provides no exact data of the evaluation results (e.g. results are only in graphical form) \cite{Wang2008,Wang2010,Xu2010,Kuo2009,Li2008,Xia2008,Zhou2011,Wu2011,Zhu2009,Karimzadehgan2011,Swersky2012,Pan2011,Ni2008,Ciaramita2008,Stewart2012,Petterson2009,Agarwal2010,Chang2009,Qin2008c,Adams2011,Sculley2009,Huang2008,Alejo2010,Sun2011,He2010b,Benbouzid2012,Geng2012,Chen2012,Xu2012,Shivaswamy2011}
\item The study reported evaluation results in a different metric than the metrics chosen for this meta-analysis \cite{Yu2009,Thuy2009,Pahikkala2009,Kersting2009,Mohan2011}
\item The study reported a higher performance on baseline methods than official benchmark runs \cite{Dubey2009,Banerjee2009,Peng2010b,Song2014,Bian2010,Bian2010b,Carvalho2008,Acharyya2012,Peng2010b,Tran2012,Asadi2013c}
\item The study did not report any baseline performance that allowed us to check validity of the results \cite{Chakrabarti2008,Wang2012b,Buffoni2011}.
\end{enumerate}

\section{A Methodology for Comparing Learning to Rank Methods Cross-Benchmark}
Qin et al. \cite{Qin2010} state that it may differ between datasets what the most accurate ranking methods are. They propose a measure they call \emph{Winning Number} to evaluate the overall performance of learning to rank methods over the multiple datasets in the LETOR 3.0 collection. Winning Number is defined as the number of other algorithms that an algorithm can beat over the set of datasets, or more formally\\

$\text{WN}_i(M) = \sum\nolimits_{j=1}^n \sum\nolimits_{k=1}^m I_{\{M_i(j)>M_k(j)\}}$\\

@@

$I_{\{M_i(j)>M_k(j)\}} = \begin{cases}
1 & \text{if } M_i(j) > M_k(j), \\
0 & \text{otherwise}
\end{cases}$\\

@@

$I^{'}_{M_i(j)>M_k(j)} = \begin{cases}
1 & \parbox[t]{5cm}{if $M_i(j)$ and $M_k(j)$ are both defined and $M_i(j) > M_k(j)$,}\\
0 & \parbox[t]{5cm}{otherwise}
\end{cases}$\\

@@

\noindent
where $IWN$ is the Ideal Winning Number, defined as\\

@@

$D_{\{M_i(j),M_k(j)\}} = \begin{cases}
1 & \text{if } M_i(j) \text{ and } M_k(j) \text{ are both defined}, \\
0 & \text{otherwise}
\end{cases}$\\

@@

\section{Results of Learning to Rank Comparison}
The following subsections provide the performance of learning to rank methods in terms of NWN for NDCG@$\{3,5,10\}$ and MAP. Performance of the learning to rank methods is plotted with NWN on the vertical axis and the number of datasets on which the method has been evaluated on the horizontal axis. Moving to the right, certainty on the performance of the method increases. The methods for which it holds that there is no other method that has 1) a higher NWN and 2) a higher number datasets evaluated, are identified as the best performing methods and are labeled. Table \ref{tab:raw_data} in the appendix provides raw NWN data for the learning to rank methods at NDCG@$\{3,5,10\}$ and MAP and their cross-metric weighted average.

\subsection{NDCG@3}
\begin{figure}
\centering
\includegraphics[scale=0.19]{gfx/ndcg3_winnum}
\caption{NDCG@3 comparison of 87 learning to rank methods}
\label{fig:normalized_winning_number_ndcg3}
\end{figure}
Figure \ref{fig:normalized_winning_number_ndcg3} shows the NWN of learning to rank methods based on NDCG@3 results. LambdaNeuralRank and CoList both acquired a NWN score of 1.0 by beating all other algorithms on one dataset, with LambdaNeuralRank winning on the AOL dataset and CoList winning on Yahoo Set 2. LARF and LRUF scored very high scores of near 1.0 on three of the LETOR 3.0 datasets, which results in more certainty on these methods' performance because they are validated on three datasets that additionally are more relevant than AOL and Yahoo Set 2 (number of evaluation results for LETOR 3.0 are higher than those for AOL and Yahoo set 2). FenchelRank, OWPC, SmoothRank, DCMP and ListNet are ordered decreasingly by NWN and at the same time increasingly in number of datasets that they are evaluated on, resulting in a higher degree of certainty on the accuracy of the algorithms.\\

@@

\subsection{NDCG@5}
\begin{figure}
\includegraphics[scale=0.19]{gfx/ndcg5_winnum}
\caption{NDCG@5 comparison of 87 learning to rank methods}
\label{fig:normalized_winning_number_ndcg5}
\end{figure}
Figure \ref{fig:normalized_winning_number_ndcg5} shows the NWN of learning to rank methods based on NDCG@5 results. LambdaNeuralRank again beat all other methods solely with results on the AOL dataset scoring a NWN of 1.0. LARF, LRUF, FenchelRank, SmoothRank, DCMP and ListNet are from left to right evaluated on an increasing number of datasets, but score decreasingly well in terms of NWN. These results are highly in agreement with the NDCG@3 comparison. The only modification compared to the NDCG@3 comparison being that OWPC did show to be a method for which there were no methods performing better on both axes in the NDCG@5 comparison, but not in the @3 comparison. Like in the NDCG@3 comparison, SmoothRank and ListNet can be regarded as most reliable results because the evaluation measurements for these methods are based on LETOR official baselines.

\subsection{NDCG@10}
\begin{figure}
\centering
\includegraphics[scale=0.19]{gfx/ndcg10_winnum}
\caption{NDCG@10 comparison of 87 learning to rank methods}
\label{fig:normalized_winning_number_ndcg10}
\end{figure}

@@

\subsection{MAP}
\begin{figure}
\centering
\includegraphics[scale=0.19]{gfx/map_winnum}
\caption{MAP comparison of 87 learning to rank methods}
\label{fig:normalized_winning_number_map}
\end{figure}
Figure \ref{fig:normalized_winning_number_map} shows the NWN of learning to rank methods based on MAP results. Comparisons on the NDCG metrics where highly in agreement on the best performing algorithms, MAP-based NWN results show different results. RankDE scores a NWN of 1.0 on one dataset, which is achieved by obtaining highest MAP-score on the LETOR 2.0 TD2003 which has many evaluation results are evaluated.\\

@@

\subsection{Cross-Metric}
\begin{figure}
\centering
\includegraphics[scale=0.21]{gfx/combined_normalized_winnum}
\caption{Cross-benchmark comparison of 87 learning to rank methods}
\label{fig:normalized_winning_number_all}
\end{figure}
Figure \ref{fig:normalized_winning_number_all} shows the NWN as function of IWN for the methods described in Table 4. The cross-metric comparison is based on the NDCG@$\{3,5,10\}$ and MAP comparisons combined, which justifies analyzing the comparison more thoroughly. Figure \ref{fig:normalized_winning_number_all} labels the algorithms with no other algorithm having a higher value on both the horizontal axis and vertical axis, but also labels the algorithms with exactly one algorithm having a higher value on both axes with smaller font size. In addition, Linear Regression and the ranking method of simply sorting on the best single feature are labelled as baselines.\\

@@

\section{Limitations}
In the NWN calculation, the weight of each benchmark on the total score is determined by the number of evaluation measurements on this benchmark. By calculating it in this way, we implicitly make the assumption that the learning to rank methods are (approximately) distributed uniformly over the benchmarks, such that the average learning to rank method tested are approximately equally hard for each data set. It could be the case however that this assumption is false and that the accurateness of the learning to rank methods on a dataset is not dataset independent.\\

@@

\section{Contributions}
We proposed a new way of comparing learning to rank methods based on sparse evaluation results data on a set of benchmark datasets. Our comparison methodology comprises of two components: 1) NWN, which provides insight in the ranking accuracy of the learning to rank method, and 2) IWN, which gives insight in the degree of certainty concerning the performance of the ranking accuracy.\\

@@

More evaluation runs are needed for the methods on the left side of Figure \ref{fig:normalized_winning_number_all}. Our work contributes to this by identifying promising learning to rank methods that researchers could focus on in performing additional evaluation runs.
%
% The following two commands are all you need in the
% initial runs of your .tex file to
% produce the bibliography for the citations in your paper.
\balance
\bibliographystyle{abbrv}
{\scriptsize\bibliography{Bibliography}}
\onecolumn
% sigproc.bib is the name of the Bibliography in this case
% You must have a proper ".bib" file
%  and remember to run:
% latex bibtex latex latex
% to resolve all references
%
% ACM needs 'a single self-contained file'!
%
%APPENDICES are optional
\appendix

@@

@@

\begin{longtable}[!hpt]{@{}lrrrrrrrrrrrrrrrr@{}}\toprule

>>>>

\documentclass{llncs}
\usepackage{llncsdoc}
\usepackage{booktabs}
\usepackage{multicol}
\usepackage{amsmath}
\usepackage{longtable}
\usepackage{times}
\usepackage{graphicx}
\usepackage{dblfloatfix}
\usepackage{fixltx2e}
\usepackage{enumitem}
\usepackage{float}
\renewcommand{\dblfloatpagefraction}{2.0}
\usepackage{array}
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\usepackage{balance}

\begin{document}
\title{A Cross-Benchmark Comparison of 87 Learning to Rank Methods}
\author{First Author\inst{1,2} \and Second Author\inst{1} \and Third Author\inst{2}}
\authorrunning{First Author et al.} % abbreviated author list (for running head)

%%%% list of authors for the TOC (use if author list has to be modified)
\tocauthor{First Author, Second Author, Third Author}
\institute{Blinded Institute 1, Adress Line 1, Address Line 2, County\\
\and
Blinded Institute 2, Address Line 1, Address Line 2, Country}
%\author{Niek Tax\inst{1,2} \and Sander Bockting\inst{1} \and Djoerd Hiemstra\inst{2}}
%
%\authorrunning{Niek Tax et al.} % abbreviated author list (for running head)
%
%%%% list of authors for the TOC (use if author list has to be modified)
%\tocauthor{Niek Tax, Sander Bockting, Djoerd Hiemstra}
%
%\institute{Avanade Netherlands B.V., Versterkerstraat 6, 1322 AP Almere, the Netherlands\\
%\email{niek.tax@avanade.com},\\
%\and
%University of Twente, P.O. Box 217, 7500AE Enschede, the Netherlands}
\maketitle
\begin{abstract}
Learning to rank is an increasingly important scientific field that comprises the use of machine learning for the ranking task. New learning to rank methods are generally evaluated on benchmark test collections. However, comparison of learning to rank methods based on evaluation results is hindered by non-existence of a standard set of evaluation benchmark collections. In this paper we propose a way to compare learning to rank methods based on a sparse set of evaluation results on a set of benchmark datasets. Our comparison methodology consists of two components: 1) Normalized Winning Number, which gives insight in the ranking accuracy of the learning to rank method, and 2) Ideal Winning Number, which gives insight in the degree of certainty concerning its ranking accuracy. Evaluation results of 87 learning to rank methods on 20 well-known benchmark datasets are collected through a structured literature search. ListNet, SmoothRank, FenchelRank, FSMRank, LRUF and LARF are the best performing learning to rank methods in increasing order of Normalized Winning Number and decreasing order of Ideal Winning Number.
\end{abstract}

@@

\section{Introduction}
Ranking is a core problem in the field of information retrieval. The ranking task in information retrieval entails the ranking of candidate documents according to their relevance to a given query. Ranking has become a vital part of web search, where commercial search engines help users find their need in the extremely large collection of the World Wide Web. Among useful applications outside web search are automatic text summarization, machine translation, drug discovery and determining the ideal order of maintenance operations \cite{Rudin2009}. In addition, the ranking task has been argued to be a better fit for recommender systems than the regression task \cite{McNee2006} (which concerns predictions on a continuous scale) that is currently frequently used in such systems.\\

@@

\vspace{-0.08in}
\section{Collecting Evaluation Results}
\label{sec:collecting_evaluation_results}
We collect evaluation results on the datasets of benchmark collections through a structured literature search. Table \ref{tbl:ltr_benchmark_collections} presents an overview of the benchmark collections included in the meta-analysis.
\begin{table}
\centering
\caption{Included learning to rank evaluation benchmark collections}
\label{tbl:ltr_benchmark_collections}
\begin{tabular}{p{4.2cm}R{1.26cm}|p{4.2cm}R{1.26cm}}\toprule
Benchmark collection & \# of datasets & Benchmark collection& \# of datasets\\
AOL		  & 1 & MSLR	  & 2\\
LETOR 2.0 & 3 & WCL2R	  & 2\\
LETOR 3.0 & 7 & Yahoo! Learning to Rank Challenge 	     & 2\\
LETOR 4.0 & 2 &Yandex Internet Mathematics 2009 contest & 1\\
\textbf{Total} & \textbf{20}&&\\ 	
\end{table}

@@

LETOR 1.0 and 3.0, Yahoo! Learning to Rank Challenge, WCL2R and AOL have accompanying papers that were released with the collection. Authors publishing evaluation results on these benchmark collections are requested to cite these papers. We collect evaluation measurements of learning to rank methods on these benchmark collections through forward literature search. Table~\ref{tbl:ltr_benchmark_forref} presents an overview of the results of this forward literature search performed using Google Scholar.
\begin{table}
\centering
\caption{Forward references of learning to rank benchmark papers}
\label{tbl:ltr_benchmark_forref}
\begin{tabular}{p{2cm}p{1.8cm}R{1.5cm}|p{3cm}p{1.9cm}R{1.6cm}}\toprule
Benchmark & Paper & \# of forward references & Benchmark & Paper & \# of forward references \\
LETOR 1.0 \& 2.0 & Liu et al. \cite{Liu2007b} & 307 & Yahoo! LtR Challenge & Chapelle et al. \cite{Chapelle2011a} & 102\\
LETOR 3.0 & Qin et al. \cite{Qin2010} & 105 & WCL2R & Alc{\^a}ntara et al. \cite{Alcantara2010} & 2\\
AOL dataset & Pass et al. \cite{Pass2006} & 339 &&\\
\end{table}
The LETOR 4.0, MSLR-web10/30k and Yandex Internet Mathematics Competition 2009 benchmark collections are not accompanied by a paper. To collect evaluation results for learning to rank methods on these benchmarks, a Google Scholar search is performed on the name of the benchmark. The literature search queries returned the following numbers of results:
\begin{description}[noitemsep,nolistsep]
\item["LETOR 4.0":]75
\item["MSLR-web10k":]16
\item["MSLR-web30k":]15
\item["Yandex Internet Mathematics":]3
\end{description}
\vspace{-0.08in}
\subsection{Literature Selection}
Table 4 in the appendix gives an overview of the learning to rank methods for which evaluation results were found through the described procedure. Occurrences of L2, L3 and L4 in Table 4 imply that these algorithms are evaluated as official LETOR 2.0, 3.0 and 4.0 baselines respectively.\\

@@

\begin{enumerate}[noitemsep,nolistsep]
\item A different evaluation methodology was used in the study compared to what was used in other studies using the same benchmark \cite{Geng2011,Lin2012}
\item The study focuses on a different learning to rank task (e.g. rank aggregation or transfer ranking) \cite{De2011,De2010,Derhami2013,De2012,Chen2010,Ah-Pine2008,Wang2009c,De2013,Miao2013,Hoi2008,De2012b,Duh2011b,Argentini2012,Qin2010c,Volkovs2013,Desarkar2011,Pan2013,Lin2011b,Volkovs2012,Dammak2011}
\item The study used an altered version of a benchmark that contained additional features \cite{Bidoki2009,Ding2010}
\item The study provides no exact data of the evaluation results (e.g. results are only in graphical form) \cite{Wang2008,Wang2010,Xu2010,Kuo2009,Li2008,Xia2008,Zhou2011,Wu2011,Zhu2009,Karimzadehgan2011,Swersky2012,Pan2011,Ni2008,Ciaramita2008,Stewart2012,Petterson2009,Agarwal2010,Chang2009,Qin2008c,Adams2011,Sculley2009,Huang2008,Alejo2010,Sun2011,He2010b,Benbouzid2012,Geng2012,Chen2012,Xu2012,Shivaswamy2011}
\item The study reported evaluation results in a different metric than the metrics chosen for this meta-analysis \cite{Yu2009,Thuy2009,Pahikkala2009,Kersting2009,Mohan2011}
\item The study reported a higher performance on baseline methods than official benchmark runs \cite{Dubey2009,Banerjee2009,Peng2010b,Song2014,Bian2010,Bian2010b,Carvalho2008,Acharyya2012,Peng2010b,Tran2012,Asadi2013c}
\item The study did not report any baseline performance that allowed us to check validity of the results \cite{Chakrabarti2008,Wang2012b,Buffoni2011}.
\end{enumerate}
\vspace{-0.08in}
\section{A Methodology for Comparing Learning to Rank Methods Cross-Benchmark}
Qin et al. \cite{Qin2010} state that it may differ between datasets what the most accurate ranking methods are. They propose a measure they call \emph{Winning Number} to evaluate the overall performance of learning to rank methods over the multiple datasets in the LETOR 3.0 collection. Winning Number is defined as the number of other algorithms that an algorithm can beat over the set of datasets, or more formally\\
$\mbox{WN}_i(M) = \sum\nolimits_{j=1}^n \sum\nolimits_{k=1}^m I_{\{M_i(j)>M_k(j)\}}$\\

@@

$I_{\{M_i(j)>M_k(j)\}} = \begin{cases}
1 & \mbox{if } M_i(j) > M_k(j), \\
0 & \mbox{otherwise}
\end{cases}$\\

@@

$I^{'}_{M_i(j)>M_k(j)} = \begin{cases}
1 & \parbox[t]{5cm}{if $M_i(j)$ and $M_k(j)$ are both defined and $M_i(j) > M_k(j)$,}\\
0 & \parbox[t]{5cm}{otherwise}
\end{cases}$\\

@@

\noindent
where $IWN$ is the Ideal Winning Number, defined as\\

@@

$D_{\{M_i(j),M_k(j)\}} = \begin{cases}
1 & \text{if } M_i(j) \text{ and } M_k(j) \text{ are both defined}, \\
0 & \text{otherwise}
\end{cases}$\\

@@

\section{Results of Learning to Rank Comparison}
The following subsections provide the performance of learning to rank methods in terms of NWN for NDCG@$\{3,5,10\}$ and MAP. Performance of the learning to rank methods is plotted with NWN on the vertical axis and the number of datasets on which the method has been evaluated on the horizontal axis. Moving to the right, certainty on the performance of the method increases. The methods for which it holds that there is no other method that has 1) a higher NWN and 2) a higher number datasets evaluated, are identified as the best performing methods and are labeled. Table \ref{tab:raw_data} in the appendix provides raw NWN data for the learning to rank methods at NDCG@$\{3,5,10\}$ and MAP and their cross-metric weighted average.
\subsection{NDCG@3}
Figure \ref{fig:normalized_winning_number_ndcg3} shows the NWN of learning to rank methods based on NDCG@3 results. LambdaNeuralRank and CoList both acquired a NWN score of 1.0 by beating all other algorithms on one dataset, with LambdaNeuralRank winning on the AOL dataset and CoList winning on Yahoo Set 2. LARF and LRUF scored very high scores of near 1.0 on three of the LETOR 3.0 datasets, which results in more certainty on these methods' performance because they are validated on three datasets that additionally are more relevant than AOL and Yahoo Set 2 (number of evaluation results for LETOR 3.0 are higher than those for AOL and Yahoo set 2). FenchelRank, OWPC, SmoothRank, DCMP and ListNet are ordered decreasingly by NWN and at the same time increasingly in number of datasets that they are evaluated on, resulting in a higher degree of certainty on the accuracy of the algorithms.
\begin{figure}[h]
\centering
\includegraphics[scale=0.19]{gfx/ndcg3_winnum}
\caption{NDCG@3 comparison of 87 learning to rank methods}
\label{fig:normalized_winning_number_ndcg3}
\end{figure}
\vspace{-0.08in}

@@

\subsection{NDCG@5}
Figure \ref{fig:normalized_winning_number_ndcg5} shows the NWN of learning to rank methods based on NDCG@5 results. LambdaNeuralRank again beat all other methods solely with results on the AOL dataset scoring a NWN of 1.0. LARF, LRUF, FenchelRank, SmoothRank, DCMP and ListNet are from left to right evaluated on an increasing number of datasets, but score decreasingly well in terms of NWN. These results are highly in agreement with the NDCG@3 comparison. The only modification compared to the NDCG@3 comparison being that OWPC did show to be a method for which there were no methods performing better on both axes in the NDCG@5 comparison, but not in the @3 comparison. Like in the NDCG@3 comparison, SmoothRank and ListNet can be regarded as most reliable results because the evaluation measurements for these methods are based on LETOR official baselines.
\vspace{-0.08in}
\begin{figure}
\centering
\includegraphics[scale=0.19]{gfx/ndcg5_winnum}
\caption{NDCG@5 comparison of 87 learning to rank methods}
\label{fig:normalized_winning_number_ndcg5}
\end{figure}
\vspace{-0.2in}
\subsection{NDCG@10}

@@

\vspace{-0.08in}
\begin{figure}
\centering
\includegraphics[scale=0.19]{gfx/ndcg10_winnum}
\caption{NDCG@10 comparison of 87 learning to rank methods}
\label{fig:normalized_winning_number_ndcg10}
\end{figure}
\vspace{-0.1in}
\subsection{MAP}
Figure \ref{fig:normalized_winning_number_map} shows the NWN of learning to rank methods based on MAP results. Comparisons on the NDCG metrics where highly in agreement on the best performing algorithms, MAP-based NWN results show different results. RankDE scores a NWN of 1.0 on one dataset, which is achieved by obtaining highest MAP-score on the LETOR 2.0 TD2003 which has many evaluation results are evaluated.
\begin{figure}
\centering
\includegraphics[scale=0.19]{gfx/map_winnum}
\caption{MAP comparison of 87 learning to rank methods}
\label{fig:normalized_winning_number_map}
\end{figure}

@@

\subsection{Cross-Metric}
Figure \ref{fig:normalized_winning_number_all} shows the NWN as function of IWN for the methods described in Table 4. The cross-metric comparison is based on the NDCG@$\{3,5,10\}$ and MAP comparisons combined, which justifies analyzing the comparison more thoroughly. Figure \ref{fig:normalized_winning_number_all} labels the algorithms with no other algorithm having a higher value on both the horizontal axis and vertical axis, but also labels the algorithms with exactly one algorithm having a higher value on both axes with smaller font size. In addition, Linear Regression and the ranking method of simply sorting on the best single feature are labelled as baselines.
\begin{figure}
\centering
\includegraphics[scale=0.21]{gfx/combined_normalized_winnum}
\caption{Cross-benchmark comparison of 87 learning to rank methods}
\label{fig:normalized_winning_number_all}
\end{figure}
\vspace{-0.1in}

@@

\section{Limitations}
In the NWN calculation, the weight of each benchmark on the total score is determined by the number of evaluation measurements on this benchmark. By calculating it in this way, we implicitly make the assumption that the learning to rank methods are (approximately) distributed uniformly over the benchmarks, such that the average learning to rank method tested are approximately equally hard for each data set. It could be the case however that this assumption is false and that the accurateness of the learning to rank methods on a dataset is not dataset independent.\\

@@

\section{Contributions}
We proposed a new way of comparing learning to rank methods based on sparse evaluation results data on a set of benchmark datasets. Our comparison methodology comprises of two components: 1) NWN, which provides insight in the ranking accuracy of the learning to rank method, and 2) IWN, which gives insight in the degree of certainty concerning the performance of the ranking accuracy.\\

@@

More evaluation runs are needed for the methods on the left side of Figure \ref{fig:normalized_winning_number_all}. Our work contributes to this by identifying promising learning to rank methods that researchers could focus on in performing additional evaluation runs.
\bibliographystyle{splncs03}
\bibliography{Bibliography}

\newpage
\section{Appendix}
\vspace{-0.3in}

@@

\centering
{\fontsize{7.6}{6.9}\selectfont
\caption{Learning to rank algorithms with measurements on benchmark datasets}

@@

\vspace{-0.3in}
{\fontsize{7.6}{6.9}\selectfont
\centering
\begin{longtable}[!hpt]{@{}lrrrrrrrrrrrrrrrr@{}}
\toprule
